Doppler Imaging Fun

### 2019-06-06 tex/ms.tex
added some equations

% Introduction
\section*{Placeholder}
\label{sec:intro}
%
See Figure~\ref{fig:pretty_function}.
%
\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.5\linewidth]{figures/pretty_function.pdf}
    \oscaption{pretty_function}{%
        This is a plot of a pretty function. And at the end of this
        caption is a symbol with a link to the \emph{exact} script
        that generated it, hosted on \textsf{GitHub}.
        \label{fig:pretty_function}
    }
    \end{centering}
\end{figure}
%

This is an equation with a ``proof'' in the form of a \textsf{Jupyter} notebook:
%
\begin{proof}{euler}
    \label{eq:euler}
    e^{i\pi} + 1 = 0.
\end{proof}
%

Check out \citet{Luger2018} and stuff.

>>>>

%
\section{Introduction}
Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.

%
\section{The equation}
\label{sec:the_equation}

In the most general form, the Doppler-shifted intensity observed at wavelength $\lambda$ at
position $x, y$ on the surface of the star at time $t$ is
%
\begin{align}
    I(\lambda, \beta, x, y, t) &=
        I\big(\lambda, 0, x, y, t\big) \nonumber \\
        &+ \frac{\mathrm{d}I(\lambda, \beta, x, y, t)}{\mathrm{d}\beta} \Big|_{\beta=0} \Delta\beta(x, y) \nonumber \\
        &+ \frac{\mathrm{d}^2I(\lambda, \beta, x, y, t)}{\mathrm{d}\beta^2} \Big|_{\beta=0} \Delta\beta^2(x, y) \nonumber \\
        &+ ...
\end{align}
%
where $\beta \equiv \frac{v}{c}$ is the relativistic parameter for a radial velocity $v$ on the surface.

% 
\section{Differentiating the spectrum}
\label{sec:derivatives}
The derivatives of the spectrum $I(\lambda)$ with respect to the relativistic parameter
$\beta$ are found by application of Fa\`a di Bruno's formula for taking high
order derivatives of the chain rule:
%
\begin{proof}{faa_di_bruno}
    \label{eq:dIdbeta}
    \frac{\mathrm{d}^n I(\lambda, \beta)}{\mathrm{d}\beta^n} \Big|_{\beta=0} &=
    \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda_0)}{\mathrm{d}\lambda_0^k} \Big|_{\lambda_0=\lambda} \lambda^k P_{nk}
\end{proof}
%
where
%
\begin{proof}{faa_di_bruno}
    \label{eq:Pnk}
    P_{nk} \equiv B_{n, k}\Bigg( \Big\{(-1)^j j! \Big\}_{j=1}^{n - k + 1} \Bigg)
\end{proof}
%
and $B_{n, k}$ is the incomplete Bell polynomial. The quantity
$\frac{\mathrm{d}^k I(\lambda_0)}{\mathrm{d}\lambda_0^k} \Big|_{\lambda_0=\lambda}$
is just the $k^\mathrm{th}$ derivative of the spectrum with respect to wavelength in the
rest frame, and must either be inferred from the data or computed numerically
from the spectrum.
